Total Platform Cyber Protection

### 2016-05-31 paper.tex
finished proof-reading till 4.1

Many different hardware contain firmware, for instance the boot BIOS
on a motherboard is a form of firmware, embedded systems often contain
specific firmware, hardware peripheral such as network cards contain
firmware as well. We consider all such areas as firmware.

The key traits of firmware is that, although it is binary code, it is
operating/interacting directly with the hardware, so there are no
OS-style abstraction layers such as virtual memory, well-defined
system calls, or hardware abstraction. Therefore, each firmware is
binary code with is specifically tailed to a specific hardware
platform.

Due to the hardware-specific nature of firmware, \emph{reverse
  engineering} is critical to understanding the firmware. In addition,
reverse engineering is particularly difficult because source code is
frequently unavailable, and, vendors desire to protect their
intellectual property, therefore, they actively obfuscate their
firmware. All this means that, extracting semantically useful
information from firmware is a key first step to performing any
security analysis of the firmware.

@@

Vulnerabilities in the firmware code allow an attacker to execute
arbitrary code with the permissions of the firmware. The class of
vulnerabilities are not unique to firmware, as they are the same class
of vulnerabilities that infect traditional binary software (buffer
overflows, logic flaws, etc.). However, firmware typically has full
control over the entire computing system, therefore vulnerabilities in
firmware are much more severe than those in the application layer. In
addition, if an attacker is able to persist their exploit, because the
compromise occurs at such a low layer of the computing system, the
attacker can persist \emph{even after reinstalling the operating
  system or application}.

The attack surface for firmware varies depending on where it is used.
In the most general case, the attacks can come from the upper layers,
specifically the Operating System or Hypervisor layers, as these are
the layers of the computing stack that can directly communicate to the
firmware. However, other firmware can be attacked either directly
through the Hardware layer itself, or through the data being
transmitted through the firmware from the hardware. For instance, a
network card firmware could be attacked through network traffic that
the firmware processes.

>>>>

Many different hardware contain firmware, for instance the boot BIOS
on a motherboard is a form of firmware, embedded systems often contain
specific firmware, hardware peripherals such as network cards contain
firmware as well. We consider all such areas as firmware.

The key traits of firmware is that, although it is binary code, it is
operating/interacting directly with the hardware, so there are no
OS-style abstraction layers such as virtual memory, well-defined
system calls, or hardware abstraction. Therefore, each firmware is
binary code which is specifically tailored to a specific hardware
platform.

Due to the hardware-specific nature of firmware, \emph{reverse
  engineering} is critical to understanding the firmware. In addition,
reverse engineering is particularly difficult because source code is
frequently unavailable, and vendors desire to protect their
intellectual property makes them actively obfuscate their
firmware. All this means that, extracting semantically useful
information from firmware is a key first step to performing any
security analysis of the firmware.

@@

Vulnerabilities in the firmware code allow an attacker to execute
arbitrary code with the permissions of the firmware. The class of
vulnerabilities are not unique to firmware, as they are the same class
of vulnerabilities that infect traditional binary software (buffer
overflows, logic flaws, etc.). However, firmware typically has full
control over the entire computing system, therefore vulnerabilities in
firmware are much more severe than those in the application layer. In
addition, if an attacker is able to persist their exploit --- because the
compromise occurs at such a low layer of the computing system --- the
attacker can persist \emph{even after reinstalling the operating
  system or application}.

The attack surface for firmware varies depending on where it is used.
In the most general case, the attacks can come from the upper layers,
specifically the Operating System or Hypervisor layers, as these are
the layers of the computing stack that can directly communicate with the
firmware. However, other firmware can be attacked either directly
through the Hardware layer itself, or through the data being
transmitted through the firmware from the hardware. For instance, a
network card firmware could be attacked through network traffic that
the firmware processes.
